Note on: Out-of-Sample Error for Laplacian Eigenmaps

### 2021-03-04 manuscripts/laplacian_eigenmaps/laplacian_eigenmaps_regression.tex
Completed section on manifold adaptivity of Laplacian Eigenmaps.

\paragraph{Estimation.} When the graph radius $\varepsilon$ and number of eigenvectors $K$ are chosen appropriately, the estimator $\wh{f}$ has (in-sample) optimal risk (up to constant factors) $\|\wh{f} - f_0\|_n^2 \lesssim n^{-2/(2 + d)}$. 
\begin{enumerate}[label=(A\arabic*)]
	\setcounter{enumi}{3}
	\item 
	\label{asmp:parameters_estimation_fo} 
	The graph radius $\varepsilon$ and the number of eigenvectors $K$ satisfy the following inequalities:
	\begin{equation}\\
	\label{eqn:radius_fo} 
	C_0 \biggl(\frac{\log n}{n}\biggr)^{1/d} \leq \varepsilon \leq \min\{i_0,K^{-1/d}\},
	\end{equation}
	and 
	\begin{equation}
	\label{eqn:eigenvector_estimation_fo} 
	c_1 (M^2 n)^{2d/(2 + d)}\leq K \leq C_1 (M^2 n)^{2d/(2 + d)}.
	\end{equation}
\end{enumerate}
\begin{theorem}
	\label{thm:laplacian_eigenmaps_estimation_fo}
	Suppose $f_0 \in H^1(P,M)$. If the Laplacian eigenmaps estimator $\wh{f}$ is computed with parameters $\varepsilon$ and $K$ that satisfy~\ref{asmp:parameters_estimation_fo}, then the following statement holds for any $\delta \in (0,1)$: with probability at least $1 - \delta - \textcolor{red}{(???)}$,
	\begin{equation}
	\label{eqn:laplacian_eigenmaps_estimation_fo}
	\|\wh{f} - f_0\|_n^2 \leq \frac{C}{\delta}M^{2d/(2 + d)}n^{-2/(2 + d)}
	\end{equation}
\end{theorem}
Some remarks:
\begin{itemize}
	\item Regarding the restrictions on hyperparameters: the lower bound on $\varepsilon$ is the connectivity threshold, the smallest length scale at which the resulting graph will still, with high probability, be connected. On the other hand, as we will see in Section~\ref{sec:analysis}, the upper bound on $\varepsilon$ is needed to ensure that the graph eigenvalue $\lambda_K \asymp \lambda_K(\Delta_P) \asymp K^{2/d}$. Finally, the restriction $K \asymp (M^2n)^{2d/(2 + d)}$ is chosen  to optimally trade-off bias and variance. Together, these restrictions suggest that the 
	\item \textbf{(1.1) How to tune hyper-parameters.} We note that the ranges~\eqref{eqn:radius_fo} and~\eqref{eqn:eigenvector_estimation_fo} depend on unknown quantities such as the dimension $d$ and radius of the Sobolev ball $M$. In practice, one typically tunes hyper-parameters by sample-splitting or cross-validation. However, because the estimator $\wh{f}$ is defined only in-sample, such approaches cannot be straightforwardly applied to select the graph radius $\varepsilon$, or number of eigenvectors $K$. We return to this issue upon considering out-of-sample extensions of $\wh{f}$ later, in Section~\ref{sec:out_of_sample}.
	\item \textbf{(1.2) The dependence on failure probability can be improved.} The upper bound on in-sample risk given by Equation~\eqref{eqn:laplacian_eigenmaps_estimation_fo} depends on the pre-factor $C/\delta$, and holds with probability $1 - \delta - \textcolor{red}{(?)}$. When $f_0 \in C^1(\mc{X};M)$, we can improve these dependencies, changing the pre-factor in~\eqref{eqn:laplacian_eigenmaps_estimation_fo} to $C(1 + 1/\delta)$, and showing that the bound holds with probability at least $1 - C\delta^2/n$. 
\end{itemize}

@@

\subsection{Analysis}
\label{sec:analysis}

@@

\begin{proposition}
	\textcolor{red}{(TODO)}
	With probability at least $1 - \textcolor{red}{(?)}$,
	\begin{equation*}
	\lambda_k \geq c \cdot \min\Bigl\{\lambda_k(\Delta_P), \frac{1}{r^{2}} \Bigr\}
	\end{equation*}
\end{proposition}
By Weyl's Law, $c k^{2/d} \leq \lambda_{k}(\Delta_P) \leq Ck^{2/d}$, and as a result $\lambda_{K} \geq C\lambda_{K}(\Delta_P)$ as long as $r \geq \kappa^{-1/d}$.

@@

\begin{theorem}
	\label{thm:laplacian_eigenmaps_estimation_manifold}
	Suppose $f_0 \in H^s(\mc{X},M)$, for $s \leq 2$. Under appropriate conditions, with probability at least $1 - \delta - \textcolor{red}{(?)}$,
	\begin{equation}
	\label{eqn:laplacian_eigenmaps_estimation_manifold}
	\|\wh{f} - f_0\|_n^2 \lesssim M^{2m/(2s + m)}n^{-2s/(2s + m)}
	\end{equation}
\end{theorem}

@@

\begin{itemize}
	\item \textbf{Proof strategy.} The proofs of Theorems~\ref{thm:laplacian_eigenmaps_estimation_manifold} and~\ref{thm:laplacian_eigenmaps_testing_manifold} proceed in a similar manner to the full-dimensional setting.
	\item \textbf{Restriction on number of derivatives.} Unlike in the full-dimensional case, Theorem~\ref{thm:laplacian_eigenmaps_estimation_manifold} holds only when $s \leq 2$. Roughly speaking, we need this restriction in order to show that $L_{P,\varepsilon}^sf(x)$ is a good approximation to $\Delta_P^sf(x)$. Otherwise, the error incurred by using Euclidean distance rather than geodesic distance in~\eqref{eqn:nonlocal_laplacian} will dominate.
\end{itemize}

@@

>>>>

\paragraph{Estimation.} When the graph radius $\varepsilon$ and number of eigenvectors $K$ are chosen appropriately, the estimator $\wh{f}$ has (in-sample) optimal risk (up to constant factors) $\|\wh{f} - f_0\|_n^2 \lesssim n^{-2/(2 + d)}$. 
\begin{enumerate}[label=(A\arabic*)]
	\setcounter{enumi}{3}
	\item 
	\label{asmp:parameters_estimation_fo} 
	The graph radius $\varepsilon$ and the number of eigenvectors $K$ satisfy the following inequalities:
	\begin{equation}\\
	\label{eqn:radius_fo} 
	C_0 \biggl(\frac{\log n}{n}\biggr)^{1/d} \leq \varepsilon \leq \min\{i_0,K^{-1/d}\},
	\end{equation}
	and 
	\begin{equation}
	\label{eqn:eigenvector_estimation_fo} 
	c_1 (M^2 n)^{2d/(2 + d)}\leq K \leq C_1 (M^2 n)^{2d/(2 + d)}.
	\end{equation}
\end{enumerate}
\begin{theorem}
	\label{thm:laplacian_eigenmaps_estimation_fo}
	Suppose $f_0 \in H^1(P,M)$. If the Laplacian eigenmaps estimator $\wh{f}$ is computed with parameters $\varepsilon$ and $K$ that satisfy~\ref{asmp:parameters_estimation_fo}, then the following statement holds for any $\delta \in (0,1)$: with probability at least $1 - \delta - \textcolor{red}{(???)}$,
	\begin{equation}
	\label{eqn:laplacian_eigenmaps_estimation_fo}
	\|\wh{f} - f_0\|_n^2 \leq \frac{C}{\delta}M^{2d/(2 + d)}n^{-2/(2 + d)}
	\end{equation}
\end{theorem}
Some remarks:
\begin{itemize}
	\item Regarding the restrictions on hyperparameters: the lower bound on $\varepsilon$ is the connectivity threshold, the smallest length scale at which the resulting graph will still, with high probability, be connected. On the other hand, as we will see in Section~\ref{subsec:analysis}, the upper bound on $\varepsilon$ is needed to ensure that the graph eigenvalue $\lambda_K \asymp \lambda_K(\Delta_P) \asymp K^{2/d}$. Finally, the restriction $K \asymp (M^2n)^{2d/(2 + d)}$ is chosen  to optimally trade-off bias and variance. Together, these restrictions suggest that the 
	\item \textbf{(1.1) How to tune hyper-parameters.} We note that the ranges~\eqref{eqn:radius_fo} and~\eqref{eqn:eigenvector_estimation_fo} depend on unknown quantities such as the dimension $d$ and radius of the Sobolev ball $M$. In practice, one typically tunes hyper-parameters by sample-splitting or cross-validation. However, because the estimator $\wh{f}$ is defined only in-sample, such approaches cannot be straightforwardly applied to select the graph radius $\varepsilon$, or number of eigenvectors $K$. We return to this issue upon considering out-of-sample extensions of $\wh{f}$ later, in Section~\ref{sec:out_of_sample}.
	\item \textbf{(1.2) The dependence on failure probability can be improved.} The upper bound on in-sample risk given by Equation~\eqref{eqn:laplacian_eigenmaps_estimation_fo} depends on the pre-factor $C/\delta$, and holds with probability $1 - \delta - \textcolor{red}{(?)}$. When $f_0 \in C^1(\mc{X};M)$, we can improve these dependencies, changing the pre-factor in~\eqref{eqn:laplacian_eigenmaps_estimation_fo} to $C(1 + 1/\delta)$, and showing that the bound holds with probability at least $1 - C\delta^2/n$. 
\end{itemize}

@@

\subsection{Analysis}
\label{subsec:analysis}

@@

\begin{proposition}
	\label{prop:graph_eigenvalue}
	\textcolor{red}{(TODO)}
	With probability at least $1 - \textcolor{red}{(?)}$,
	\begin{equation*}
	\lambda_k \geq c \cdot \min\Bigl\{\lambda_k(\Delta_P), \frac{1}{r^{2}} \Bigr\}
	\end{equation*}
\end{proposition}
By Weyl's Law, $c k^{2/d} \leq \lambda_{k}(\Delta_P) \leq Ck^{2/d}$, and as a result $\lambda_{K} \geq C\lambda_{K}(\Delta_P)$ as long as $r \geq \kappa^{-1/d}$.

@@

\begin{theorem}
	\label{thm:laplacian_eigenmaps_estimation_manifold}
	Suppose $f_0 \in H^s(\mc{X},M)$, for $s \leq 4$. Under appropriate conditions, with probability at least $1 - \delta - \textcolor{red}{(?)}$,
	\begin{equation}
	\label{eqn:laplacian_eigenmaps_estimation_manifold}
	\|\wh{f} - f_0\|_n^2 \lesssim M^{2m/(2s + m)}n^{-2s/(2s + m)}
	\end{equation}
\end{theorem}

@@

\begin{itemize}
	\item \textbf{Proof strategy.} The proofs of Theorems~\ref{thm:laplacian_eigenmaps_estimation_manifold} and~\ref{thm:laplacian_eigenmaps_testing_manifold} follow very similarly to the full-dimensional setting. The difference is that when $\mc{X}$ is a manifold with intrinsic dimension $m$, we can prove analogous results to Propositions~\ref{prop:graph_seminorm} and~\ref{prop:graph_eigenvalue}, but with the ambient dimension $d$ replaced by the intrinsic dimension $m$. 
	\item \textbf{Restriction on number of derivatives.} Unlike in the full-dimensional case, our upper bound on the estimation error of $\wh{f}$ matches the minimax rate $n^{-2s/(2s + m)}$ only when $s \leq 4$. At a high level, thinking of the graph $G$ as an estimate of the manifold $\mc{X}$, we incur some error by using Euclidean distance rather than geodesic distance to form the edges of $G$. By contrast, in the full-dimensional setting the Euclidean metric exactly coincides with the geodesic distance for all points $x,z \in \mc{X}$ that are sufficiently close to each other and far from the boundary of $\mc{X}$). This extra error incurred in the manifold setting dominates when $s > 4$. We give a more detailed explanation of this phenomenon in Appendix~\ref{sec:manifold_proofs}.
	\item \textbf{Comparison with traditional spectral series estimators.} Traditional spectral series estimators achieve the minimax rate for all values of $s$ and $m$. On the other hand, as we have already discussed, their default implementation assumes a priori knowledge of the domain $\mc{X}$, which is arguably a particularly unrealistic assumption when $\mc{X}$ is assumed to be a manifold. It is not clear whether this gap between spectral series and Laplacian eigenmaps estimators---or more generally, between estimators which assume strong knowledge of the manifold, and those which do not---is real, or a product of loose upper bounds. 
\end{itemize}

@@

\appendix

\input{appendix.tex}

### 2021-03-04 notes/weekly_notes/12.24.20.NotesForWeek.tex
Completed section on manifold adaptivity of Laplacian Eigenmaps.

\section{Miscellaneous}
I put things here which did not belong in any other section.

\subsection{Proof of Lemma~\ref{lem:kernel_smoothing_bias}, $d = 1$ and $p$ uniform}
Without loss of generality take the domain $\Omega = (0,1)$. Recall that we are interested in upper bounding
\begin{equation*}
\|T_{P,\varepsilon}u - u\|_{P}^2 = \int_{\Omega} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x) \leq C\varepsilon^{2k}
\end{equation*}
where $L_{P,\varepsilon}$ is a non-local approximation to the continuum weighted Laplacian, given by
\begin{equation*}
L_{P,\varepsilon}u(x) := \frac{1}{d_P(x)}\int_{\Omega} \bigl(u(z) - u(x)\bigr) \eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dP(z).
\end{equation*}
We begin with a pointwise analysis of $L_{p,\varepsilon}u(x)$ at a given $x \in \Omega$. We may assume without loss of generality that $u \in C_0^{\infty}(\Omega)$, since $C_0^{\infty}(\Omega)$ is dense in $H_0^k(\Omega)$ and $\|T_{P,\varepsilon}u - u\|_P^2$ is continuous with respect to $\|\cdot\|_{H_0^k}$. Since $u$ is smooth, for every $x,z \in \Omega$, we have the $k$th-order Taylor expansion
\begin{equation*}
u(z) - u(x) = \sum_{j = 1}^{k - 1} (z - x)^{j} u^{(j)}(x)  + \frac{(z - x)^k}{(k - 1)!}\int_{0}^{1}(1 - t)^{k - 1}u^{(k)}(x + t(z - x))\,dt.
\end{equation*}
As a result,
\begin{equation}
\label{pf:kernel_smoothing_bias_1d_1}
\begin{aligned}
L_{P,\varepsilon}u(x) = \frac{1}{d_P(x)} & \Biggl\{\sum_{j = 1}^{k - 1} u^{(j)}(x) \int_{\Omega}(z - x)^{j}\eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr)\,dz + \\ 
& \frac{1}{(k - 1)!} \int_{\Omega} \int_{0}^{1} (1 - t)^k (z - x)^k u^{(k)}(x + t(z - x)) \eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dt \,dz \Biggr\}
\end{aligned}
\end{equation}
The way in which we use~\eqref{pf:kernel_smoothing_bias_1d_1} will depend on whether $x \in \Omega$ satisfies $B(x,\varepsilon) \subset \Omega$ or not. Let $\Omega_{\varepsilon} := \{x: B(x,\varepsilon) \in \Omega\}$ and let $\partial_{\varepsilon}\Omega := \Omega \setminus \Omega_{\varepsilon}$. Clearly
\begin{equation*}
\|L_{P,\varepsilon}u\|_{P}^2 = \underbrace{\int_{\Omega_{\varepsilon}} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_1} + \underbrace{\int_{\partial_{\varepsilon}\Omega} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_2}
\end{equation*}
and we now separately upper bound $I_1$ and $I_2$.

\paragraph{Upper bound on $I_1$.}
If $x \in \Omega_{\varepsilon}$ then all $z \in B(x,\varepsilon)$ also belong to $\Omega$. For one thing, this implies
\begin{equation*}
d_P(x) = \int_{\Omega} \eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dz = \varepsilon \cdot \int_{B(0,1)}  \eta(v) \,dv = \epsilon.
\end{equation*}
Addtionally, we have that all $j = 1,\ldots,k - 1$, 
\begin{equation*}
\int_{\Omega}(z - x)^{k}\eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dz = \varepsilon^j \cdot \int_{B(0,1)} v^j \eta(v) \,dv = 0,
\end{equation*}
where the second equality follows because $\eta$ is a $k$th-order kernel. Consequently $L_{P,\varepsilon}$ depends only on the $k$th derivative of $u$: changing variables to $v = (z - x)/\varepsilon$, we have
\begin{align*}
L_{P,\varepsilon}u(x) & = \frac{1}{\varepsilon} \cdot \frac{1}{(k - 1)!} \int_{0}^{1} \int_{\Omega} (1 - t)^k (z - x)^k u^{(k)}(x + t(z - x)) \eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dz \,dv \\
& = \frac{\varepsilon^{k}}{(k - 1)!} \int_{0}^{1} \int_{B(0,1)} (1 - t)^k v^k u^{(k)}(x + t\varepsilon v) \eta(v) \,dv \,dt.
\end{align*} 
This identity along with Jensen's inequality implies that
\begin{equation*}
\Bigl(L_{P,\varepsilon}u(x)\Bigr)^2 \leq \biggl(\frac{\varepsilon^{k}}{(k - 1)!}\biggr)^2 \cdot  \int_{0}^{1} \int_{B(0,1)} v^{2k} \bigl(u^{(k)}(x + t\varepsilon v)\bigr)^2 \eta(|v|) \,dv \,dt.
\end{equation*}
Integrating over all $x \in \Omega_{\varepsilon}$ gives an upper bound on $I_1$. 
From here, by changing the order of integration, substituting $\wt{x} = x + t\varepsilon v$, and noting that $\wt{x} \in \Omega$, we arrive at the desired bound:
\begin{align*}
I_1 & \leq \biggl(\frac{\varepsilon^{k}}{(k - 1)!}\biggr)^2 \int_{0}^{1} \int_{B(0,1)} \int_{\Omega_{\varepsilon}} v^{2k} \bigl(u^{(k)}(x + t\varepsilon v)\bigr)^2 \eta(|v|) \,dx \,dv \,dt \\
& \leq \biggl(\frac{\varepsilon^{k}}{(k - 1)!}\biggr)^2 \int_{0}^{1} \int_{B(0,1)} \int_{\Omega} v^{2k} \bigl(u^{(k)}(\wt{x})\bigr)^2 \eta(|v|) \,d\wt{x} \,dv \,dt \\
& = \biggl(\frac{\varepsilon^{k}}{(k - 1)!}\biggr)^2 |u|_{H^k(\Omega)}^2 \sigma_{\eta}.
\end{align*}

\paragraph{Upper bound on $I_2$.}

>>>>

\section{Miscellaneous}
I put things here which do not belong in any other section.

\subsection{Proof of Lemma~\ref{lem:kernel_smoothing_bias}, $d = 1$ and $p$ uniform}
Without loss of generality take the domain $\Omega = (0,1)$. Recall that we are interested in upper bounding
\begin{equation*}
\|T_{P,\varepsilon}u - u\|_{P}^2 = \int_{\Omega} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x) \leq C\varepsilon^{2k}
\end{equation*}
where $L_{P,\varepsilon}$ is a non-local approximation to the continuum weighted Laplacian, given by
\begin{equation*}
L_{P,\varepsilon}u(x) := \frac{1}{d_P(x)}\int_{\Omega} \bigl(u(z) - u(x)\bigr) \eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dP(z).
\end{equation*}
Let $\Omega_{\varepsilon} := \{x: B(x,\varepsilon) \in \Omega\}$ and let $\partial_{\varepsilon}\Omega := \Omega \setminus \Omega_{\varepsilon}$. Clearly
\begin{equation*}
\|L_{P,\varepsilon}u\|_{P}^2 = \underbrace{\int_{\Omega_{\varepsilon}} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_1} + \underbrace{\int_{\partial_{\varepsilon}\Omega} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_2}
\end{equation*}
and we now separately upper bound $I_1$ and $I_2$.

\paragraph{Upper bound on $I_1$.}
We begin with a pointwise analysis of $L_{p,\varepsilon}u(x)$ at a given $x \in \Omega_{\varepsilon}$. We may assume without loss of generality that $u \in C_0^{\infty}(\Omega)$, since $C_0^{\infty}(\Omega)$ is dense in $H_0^k(\Omega)$ and $\|T_{P,\varepsilon}u - u\|_P^2$ is continuous with respect to $\|\cdot\|_{H_0^k}$. Since $u$ is smooth, for every $x,z \in \Omega$, we have the $k$th-order Taylor expansion
\begin{equation*}
u(z) - u(x) = \sum_{j = 1}^{k - 1} (z - x)^{j} u^{(j)}(x)  + \frac{(z - x)^k}{(k - 1)!}\int_{0}^{1}(1 - t)^{k - 1}u^{(k)}(x + t(z - x))\,dt.
\end{equation*}
As a result,
\begin{equation}
\label{pf:kernel_smoothing_bias_1d_1}
\begin{aligned}
L_{P,\varepsilon}u(x) = \frac{1}{d_P(x)} & \Biggl\{\sum_{j = 1}^{k - 1} u^{(j)}(x) \int_{\Omega}(z - x)^{j}\eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr)\,dz + \\ 
& \frac{1}{(k - 1)!} \int_{\Omega} \int_{0}^{1} (1 - t)^k (z - x)^k u^{(k)}(x + t(z - x)) \eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dt \,dz \Biggr\}
\end{aligned}
\end{equation}

Now, since $x \in \Omega_{\varepsilon}$ then all $z \in B(x,\varepsilon)$ also belong to $\Omega$. For one thing, this implies
\begin{equation*}
d_P(x) = \int_{\Omega} \eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dz = \varepsilon \cdot \int_{B(0,1)}  \eta(v) \,dv = \epsilon.
\end{equation*}
Additionally, we have that all $j = 1,\ldots,k - 1$, 
\begin{equation*}
\int_{\Omega}(z - x)^{k}\eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dz = \varepsilon^j \cdot \int_{B(0,1)} v^j \eta(v) \,dv = 0,
\end{equation*}
where the second equality follows because $\eta$ is a $k$th-order kernel. Consequently $L_{P,\varepsilon}$ depends only on the $k$th derivative of $u$: changing variables to $v = (z - x)/\varepsilon$, we have
\begin{align*}
L_{P,\varepsilon}u(x) & = \frac{1}{\varepsilon} \cdot \frac{1}{(k - 1)!} \int_{0}^{1} \int_{\Omega} (1 - t)^k (z - x)^k u^{(k)}(x + t(z - x)) \eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dz \,dv \\
& = \frac{\varepsilon^{k}}{(k - 1)!} \int_{0}^{1} \int_{B(0,1)} (1 - t)^k v^k u^{(k)}(x + t\varepsilon v) \eta(v) \,dv \,dt.
\end{align*} 
This identity along with Jensen's inequality implies that
\begin{equation*}
\Bigl(L_{P,\varepsilon}u(x)\Bigr)^2 \leq \biggl(\frac{\varepsilon^{k}}{(k - 1)!}\biggr)^2 \cdot  \int_{0}^{1} \int_{B(0,1)} v^{2k} \bigl(u^{(k)}(x + t\varepsilon v)\bigr)^2 \eta(|v|) \,dv \,dt.
\end{equation*}
Integrating over all $x \in \Omega_{\varepsilon}$ gives an upper bound on $I_1$. 
From here, by changing the order of integration, substituting $\wt{x} = x + t\varepsilon v$, and noting that $\wt{x} \in \Omega$, we arrive at the desired bound:
\begin{align*}
I_1 & \leq \biggl(\frac{\varepsilon^{k}}{(k - 1)!}\biggr)^2 \int_{0}^{1} \int_{B(0,1)} \int_{\Omega_{\varepsilon}} v^{2k} \bigl(u^{(k)}(x + t\varepsilon v)\bigr)^2 \eta(|v|) \,dx \,dv \,dt \\
& \leq \biggl(\frac{\varepsilon^{k}}{(k - 1)!}\biggr)^2 \int_{0}^{1} \int_{B(0,1)} \int_{\Omega} v^{2k} \bigl(u^{(k)}(\wt{x})\bigr)^2 \eta(|v|) \,d\wt{x} \,dv \,dt \\
& = \biggl(\frac{\varepsilon^{k}}{(k - 1)!}\biggr)^2 |u|_{H^k(\Omega)}^2 \sigma_{\eta}.
\end{align*}

\paragraph{Upper bound on $I_2$.}
We will prove the upper bound
\begin{equation*}
\int_{0}^{\varepsilon} \bigl|L_{P,\varepsilon}u(x)\bigr|^2 \,dx \leq C \varepsilon^{2k},
\end{equation*}
with the bound on $\int_{1 - \varepsilon}^{1} \bigl|L_{P,\varepsilon}u\bigr|^2$ following in a completely analogous fashion.

Taking a Taylor expansion of $u$ around $0$ gives
\begin{align*}
u(x) - u(0) & = \sum_{j = 1}^{k - 1} x^j u^{(j)}(0) + \frac{1}{(k - 1)!} \int_{0}^{x}u^{(k)}(s)(x - s)^{k - 1}\,ds \\
& = \frac{1}{(k - 1)!} \int_{0}^{x}u^{(k)}(s)(x - s)^{k - 1}\,ds,
\end{align*}
with the second inequality following since $u \in C_c^{\infty}(\Omega)$ implies $u^{(j)}(0) = 0$ for $j = 1,\ldots,k - 1$. From this identity along with Jensen's inequality, we have
\begin{align*}
\int_{0}^{\varepsilon} \int_{\Omega} \bigl(u(x)\bigr)^2 \eta\biggl(\frac{z - x}{\varepsilon}\biggr) \,dz \,dx & = \int_{0}^{\varepsilon} d_{\nu}(x) \bigl(u(x)\bigr)^2 \,dx \\
& \leq \varepsilon \int_{0}^{\varepsilon} \bigl(u(x)\bigr)^2 \,dx \\
& \leq \varepsilon^{2k} \int_{0}^{\varepsilon} \int_{0}^{x} \bigl(u^{(k)}(s)\bigr)^2 \,ds \,dx. 
\end{align*}
From here, switching the order of integration and substituting $v = s/\varepsilon$ gives the desired result:
\begin{align*}
I_1 & \leq \frac{\varepsilon^{2k - 1}}{\alpha} \int_{0}^{\varepsilon} \int_{s}^{\varepsilon} \bigl(u^{(k)}(s)\bigr)^2 \,dx \,ds \\
& \leq \frac{\varepsilon^{2k + 1}}{\alpha} \int_{0}^{1} \bigl(u^{(k)}(v)\bigr)^2 \,dv \\
& = \frac{\varepsilon^{2k + 1}}{\alpha} |u|_{H^k(\Omega)}^2
\end{align*}
